plackett_luce_monster

### 2022-05-27 inst/plackett_luce_monster.Rmd
change from elastic to cheering

We will calculate a Plackett-Luce likelihood function for four runners 1,2,3,4  but with a reified
Bradley-Terry monster that corresponds
to having 1 and 2 tethered by an elastic string and 3 and 4 also tethered by an elastic string.  The string 
acts to bring the two runners together and makes it more likely that such attached runners will place consecutively.

 first do three: 1 and 2 tethered,  3 not tethered to anyone

 123: $\frac{1}{1+2+3}\cdot\frac{2+M}{2+3+M}$

 132: $\frac{1}{1+3+2}\cdot\frac{3}{3+2+M}$

 213: $\frac{2}{2+1+3}\cdot\frac{1+M}{1+3+M}$

 231: $\frac{2}{2+3+1}\cdot\frac{3}{3+1+M}$

 312: $\frac{3}{3+1+2}\cdot\frac{1}{2+1}$

 321: $\frac{3}{3+2+1}\cdot\frac{2}{2+1}$

new stuff here

new stuff here

now 1 and 2 tethered, 3 and 4 tethered.

>>>>

We will calculate a Plackett-Luce likelihood function for four runners
$\left\lbrace 1,2,3,4\right\rbrace$ but with a reified Bradley-Terry
monster that corresponds to having subsets of mutual friends who
support one another.  For example, we might have runners 1 and 2 being
friends, and runners 3 and 4 being friends: we would represent this as
$\left\lbrace\left\lbrace 1,2\right\rbrace,\left\lbrace
3,4\right\rbrace\right\rbrace$.

The statistical model is as follows.  If a runner finishes, then he
cheers on all his friends who are still running, thereby adding to
their strength.  This is a very simple form of non-independence.

First do three runners, and suppose the equivalence classes are
$\left\lbrace\left\lbrace 1,2\right\rbrace,\left\lbrace
3\right\rbrace\right\rbrace$.

 123: $\frac{p_1}{p_1+p_2+p_3}\cdot\frac{p_2+M}{p_2+p_3+M}\qquad\frac{p_1}{p_1+p_2+p_3}\cdot\frac{\lambda p_2}{\lambda p_2+p_3}$

 132: $\frac{p_1}{p_1+p_3+p_2}\cdot\frac{p_3}{p_3+p_2+M}\qquad\frac{p_1}{p_1+p_3+p_2}\cdot\frac{p_3}{p_3+\lambda p_2}$

 213: $\frac{p_2}{p_2+p_1+p_3}\cdot\frac{p_1+M}{p_1+p_3+M}\qquad\frac{p_2}{p_2+p_1+p_3}\cdot\frac{\lambda p_1}{\lambda p_1+p_3}$

 231: $\frac{p_2}{p_2+p_3+p_1}\cdot\frac{p_3}{p_3+p_1+M}$

 312: $\frac{p_3}{p_3+p_1+p_2}\cdot\frac{p_1}{p_2+p_1}$

 321: $\frac{p_3}{p_3+p_2+p_1}\cdot\frac{p_2}{p_2+p_1}$

Now four runners with classes $\left\lbrace\left\lbrace
1,2\right\rbrace,\left\lbrace 3,4\right\rbrace\right\rbrace$.
